\chapter{Objective}\label{objective}

To develop a web platform that exposes \gls{SQL} scripts to \gls{IPB}'s employees in a convenient way that does not require expert knowledge of the underlying system architecture and eases the technician workload during the institution's critical moments.

Such platform will be maintained by an administrator that is responsible for registering the desired \gls{SQL} scripts.

Based on their role in the institution, professors and other employees are presented to a list of queries coupled with meaningful title and description in which they can run, see the resulting table and download an spreadsheet file.

As a non-functional objective, the system should be easily maintained by the current Academic Systems department team and therefore should comply to their current technologies.

Following is a translation of the original proposal found in Appendix~\ref{apendice1}:
\begin{displayquote}
  Proposal nº 2

  To architect and construct from scratch a ``business intelligence'' system with emphasis on education management.
  Now a days we know how valuable and important information is for those who manage institutions and the impact that data analysis tools have in the decision-making process.
  At the time writing, \gls{IPB} is already provided of a centralized database through which a large number of \gls{SQL} of many diverse purposes queries are run.
  The intention is that, based on certain criteria, provide access to information without having to manually write queries that are often more than 30 lines long.

  The proposed system would be fed with ``clusters'' of queries and provide a way to easily insert and validate individual or group of queries depending on the currently logged-in user's profile.

  Keywords are reuse and automatic parameterization of queries that are supported by an automatic web search interface based on the current query.

  All in all, its about deploying a intelligent search system that is able to adapt to the necessities and profile of each user. The end result will always be tables of data that can be exported to many different formats
\end{displayquote}
